Single-step Hybrid Predition

### 2016-12-12 reports/transformed_kernels.Rmd
Init repeated prediction with different snp77

mrna42 <- lapply(seq_along(trans_lst), FUN = function(i) {
  mat <- trans_lst[[i]]
  high_cor_idx <- mrna_cor_idx[[i]]
  if (isTRUE(length(high_cor_idx) != 0)) {
    mat <- mat[, -high_cor_idx]
  }
  mat
})
names(mrna42) <- names(mrna_lst)

# Remove perfect LD
snp42 <- cat_lst %>% 
  transpose() %>%
  .[names(.) == "snp42"] %>%
  at_depth(.depth = 2, .f = 1) %>%
  .[[1]]

snp77 <- cat_lst %>% 
  transpose() %>%
  .[names(.) == "ped100_snp77"] %>%
  at_depth(.depth = 2, .f = 2) %>%
  .[[1]]

snp100 <- cat_lst %>%
  transpose() %>%
  .[names(.) == "snp100"] %>%
  at_depth(.depth = 2, .f = 1) %>%
  .[[1]]

@@

# Get pedigree data
ped100 <- cat_lst %>% 
  transpose() %>%
  .[names(.) == "ped100_snp77"] %>%
  at_depth(.depth = 2, .f = 1) %>%
  .[[1]]
names(ped100) <- c("Dent", "Flint")

ped42 <- cat_lst %>% 
  transpose() %>%
  .[names(.) == "ped42"] %>%
  at_depth(.depth = 2, .f = 1) %>%
  .[[1]]
names(ped42) <- c("Dent", "Flint")
```

```{r Kernel-assembly, cache = TRUE}
nms100 <- cat_lst %>%
  transpose() %>%
  .[names(.) == "ped100"] %>%
  at_depth(.depth = 2, "geno") %>%
  .[[1]]

nms42 <- cat_lst %>%
  transpose() %>%
  .[names(.) == "mrna42"] %>%
  at_depth(.depth = 2, "geno") %>%
  .[[1]]

@@

trans_cat_lst <- lapply(pred_sets, FUN = function(x) {
  cmb_lst <- x %>% 
    map(~get(.))
  names(cmb_lst) <- x
  cmb_lst <- cmb_lst %>% 
    transpose()
  largest_pred_size <- x %>%
    str_extract(., pattern = "[0-9]+") %>%
    as.integer() %>% 
    max()

@@

  cmb_lst[] <- lapply(seq_along(cmb_lst), FUN = function(i) {
    nm <- names(cmb_lst)[i]
    dat <- cmb_lst[[nm]]
    dat$geno <- hyb_names_pred_size[[nm]]
    dat
  })
  cmb_lst
})
names(trans_cat_lst) <- pred_sets %>%
  map(~paste(., collapse = "_")) %>%
  flatten_chr()
trans_cat_lst <- trans_cat_lst %>%
  transpose()
saveRDS(trans_cat_lst, 
        file = "./data/derived/transformed_pred_sub_list.RDS")

## -- BUILD KERNELS --------------------------------------------------------
# Apply kernel building functions to different predictor sets.
# The choice of function depends on the number of predictors as well as on the
# type of predictor (are pedigree data involved or not?).
ped100_snp77_mrna42 <- trans_cat_lst %>%
  transpose() %>%
  .[["ped100_snp77_mrna42"]] %>%
  map(~impute2(ped = .[[1]],
               snp = .[[2]],
               mrna = .[[3]],
               geno = .[["geno"]],
               as_kernel = TRUE,
               bglr_model = "BRR"
    )
  ) %>%
  map(2) %>%
  map("X")

snp100_mrna42 <- trans_cat_lst %>%
  transpose() %>%
  .[["snp100_mrna42"]] %>%
  map(~impute_eta(
     x = .[[1]],
     y = .[[2]],
     geno = .[["geno"]],
     as_kernel = TRUE,
     is_pedigree = FALSE,
     bglr_model = "BRR"
    )
  ) %>%
  map(2) %>%
  map("X")

ped100_x <- trans_cat_lst %>%
  transpose() %>%
  .[names(.) %in% c("ped100_mrna42", "ped100_snp77")] %>%
  at_depth(.depth = 2, .f = ~impute_eta(
    x = .[[1]],
    y = .[[2]],
    geno = .[["geno"]], 
    as_kernel = TRUE,
    is_pedigree = TRUE,
    bglr_model = "BRR"
    )
  ) %>%
  at_depth(.depth = 2, .f = 2) %>%
  at_depth(.depth = 2, .f = "X")

single_pred <- trans_cat_lst %>%
  transpose() %>%
  .[names(.) %in% c("snp42", "mrna42", "snp100")] %>%
  at_depth(.depth = 2, .f = ~complete_eta(
    x = .[[1]],
    geno = .[["geno"]],
    as_kernel = TRUE,
    is_pedigree = FALSE,
    bglr_model = "BRR"
    )
  ) %>%
  at_depth(.depth = 2, .f = 1) %>%
  at_depth(.depth = 2, .f = "X")

>>>>

mrna42 <- lapply(seq_along(trans_lst), FUN = function(i) {
  mat <- trans_lst[[i]]
  high_cor_idx <- mrna_cor_idx[[i]]
  if (isTRUE(length(high_cor_idx) != 0)) {
    mat <- mat[, -high_cor_idx]
  }
  mat
})
names(mrna42) <- names(mrna_lst)
saveRDS(mrna42, 
        file = "./data/derived/predictor_subsets/transformed-mrna42.RDS")

# Remove perfect LD
snp42 <- cat_lst %>% 
  purrr::transpose() %>%
  .[names(.) == "snp42"] %>%
  at_depth(.depth = 2, .f = 1) %>%
  .[[1]]

snp77 <- cat_lst %>% 
  purrr::transpose() %>%
  .[names(.) == "ped100_snp77"] %>%
  at_depth(.depth = 2, .f = 2) %>%
  .[[1]]

snp100 <- cat_lst %>%
  purrr::transpose() %>%
  .[names(.) == "snp100"] %>%
  at_depth(.depth = 2, .f = 1) %>%
  .[[1]]

@@

# Get pedigree data
ped100 <- cat_lst %>% 
  purrr::transpose() %>%
  .[names(.) == "ped100_snp77"] %>%
  at_depth(.depth = 2, .f = 1) %>%
  .[[1]]
names(ped100) <- c("Dent", "Flint")

ped42 <- cat_lst %>% 
  purrr::transpose() %>%
  .[names(.) == "ped42"] %>%
  at_depth(.depth = 2, .f = 1) %>%
  .[[1]]
names(ped42) <- c("Dent", "Flint")
```

```{r Kernel-assembly, cache = TRUE}
nms100 <- cat_lst %>%
  purrr::transpose() %>%
  .[names(.) == "ped100"] %>%
  at_depth(.depth = 2, "geno") %>%
  .[[1]]

nms42 <- cat_lst %>%
  purrr::transpose() %>%
  .[names(.) == "mrna42"] %>%
  at_depth(.depth = 2, "geno") %>%
  .[[1]]

@@

trans_cat_lst <- lapply(pred_sets, FUN = function(x) {
  cmb_lst <- x %>% 
    map(~get(.))
  names(cmb_lst) <- x
  cmb_lst <- cmb_lst %>% 
    purrr::transpose()
  largest_pred_size <- x %>%
    str_extract(., pattern = "[0-9]+") %>%
    as.integer() %>% 
    max()

@@

  cmb_lst[] <- lapply(seq_along(cmb_lst), FUN = function(i) {
    nm <- names(cmb_lst)[i]
    dat <- cmb_lst[[nm]]
    dat$geno <- hyb_names_pred_size[[nm]]
    dat
  })
  cmb_lst
})
names(trans_cat_lst) <- pred_sets %>%
  map(~paste(., collapse = "_")) %>%
  flatten_chr()
trans_cat_lst <- trans_cat_lst %>%
  purrr::transpose()
saveRDS(trans_cat_lst, 
        file = "./data/derived/transformed_pred_sub_list.RDS")

## -- BUILD KERNELS --------------------------------------------------------
# Apply kernel building functions to different predictor sets.
# The choice of function depends on the number of predictors as well as on the
# type of predictor (are pedigree data involved or not?).
ped100_snp77_mrna42 <- trans_cat_lst %>%
  purrr::transpose() %>%
  .[["ped100_snp77_mrna42"]] %>%
  map(~impute2(ped = .[[1]],
               snp = .[[2]],
               mrna = .[[3]],
               geno = .[["geno"]],
               as_kernel = TRUE,
               bglr_model = "BRR"
    )
  ) %>%
  map(2) %>%
  map("X")

snp100_mrna42 <- trans_cat_lst %>%
  purrr::transpose() %>%
  .[["snp100_mrna42"]] %>%
  map(~impute_eta(
     x = .[[1]],
     y = .[[2]],
     geno = .[["geno"]],
     as_kernel = TRUE,
     is_pedigree = FALSE,
     bglr_model = "BRR"
    )
  ) %>%
  map(2) %>%
  map("X")

ped100_x <- trans_cat_lst %>%
  purrr::transpose() %>%
  .[names(.) %in% c("ped100_mrna42", "ped100_snp77")] %>%
  at_depth(.depth = 2, .f = ~impute_eta(
    x = .[[1]],
    y = .[[2]],
    geno = .[["geno"]], 
    as_kernel = TRUE,
    is_pedigree = TRUE,
    bglr_model = "BRR"
    )
  ) %>%
  at_depth(.depth = 2, .f = 2) %>%
  at_depth(.depth = 2, .f = "X")

single_pred <- trans_cat_lst %>%
  purrr::transpose() %>%
  .[names(.) %in% c("snp42", "mrna42", "snp100")] %>%
  at_depth(.depth = 2, .f = ~complete_eta(
    x = .[[1]],
    geno = .[["geno"]],
    as_kernel = TRUE,
    is_pedigree = FALSE,
    bglr_model = "BRR"
    )
  ) %>%
  at_depth(.depth = 2, .f = 1) %>%
  at_depth(.depth = 2, .f = "X")
